%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}

% Use moderncv theme.
\moderncvstyle{classic}
\moderncvcolor{red}
\nopagenumbers{}

% Character encoding.
\usepackage[utf8]{inputenc}

\usepackage[load=abbr]{siunitx}

% Adjust the page margins.
\usepackage[scale=0.8]{geometry}

\usepackage[
  backend=biber,
  style=nature,
]{biblatex}
\addbibresource{publications.bib}

% Contact data.
\name{Kirill}{Bobyrev}
\title{Software Engineer}
\email{kirillbobyrev@gmail.com}
\linkedin{kirillbobyrev}
\github{kirillbobyrev}
\twitter{kirillbobyrev}
\homepage{kirillbobyrev.com}

\DeclareFieldFormat{labelnumberwidth}{}
\setlength{\biblabelsep}{0pt}

%-------------------------------------------------------------------------------
% Resume
%-------------------------------------------------------------------------------

\begin{document}

\makecvtitle

\section{Experience}
  \cventry{Nov 2019 - Present}{Software Engineer}{Google}{}{}{
    Working on \href{https://clangd.llvm.org/}{\textcolor{blue}{Clangd}},
    Clang-based C++ Language Server Protocol implementation for Visual Studio
    Code, Vim, CLion, XCode, Eclipse, a number of other IDEs and text editor
    plugins.
    \begin{itemize}
      \item Implemented remote code completion service that serves an index for
        LLVM and Chrome. This allows developers with slow machines to get
        precise code completion and navigation for these large projects.
      \item Took responsibilities of Product Manager and User Experience
        Researcher: continuously interviewed our users and processed feedback,
        built feature roadmaps and prioritized tasks based on the needs of our
        users.
      \item Lead Semantic Highlighting improvements for our Visual Studio Code
        plugin that is used by over $50\,000$ users and our Vim plugin that is
        also commonly used by Google developers.
    \end{itemize}
    }
  \cventry{Feb 2019 - Jun 2019}{Data Scientist}
  {\href{https://handl.ai/}{\textcolor{blue}{Handl}}, Y Combinator Startup}{}{}{
    Handl uses Machinhe Learning to to convert documents into structured
    data.
    \begin{itemize}
      \item Implemented state-pf-the-art Deep Learning models for Optical
        Character Recognition in PyTorch and TensorFlow.
      \item Secured a contract with AMG Mercedes Benz, worked out how to
        translate their business goals into fine-grained technical problems and
        lead the project.
      \item Built models Image and Sound Segmentation, Image Classification and
        Video Fraud Detection for our clients.
    \end{itemize}
    }
  \cventry{Jul 2018 - Sep 2018}{Software Engineering Intern}
    {Google}{}{C++ Language Tools Team}
    {Significantly improved C++ code completion for large projects.
     \begin{itemize}
       \item Designed and implemented
         \href{https://docs.google.com/document/d/1C-A6PGT6TynyaX4PXyExNMiGmJ2jL1UwV91Kyx11gOI/edit?usp=sharing}
         {\textcolor{blue}{Dex}} -- efficient Clangd symbol index for fuzzy
         matching code completion based on Russ Cox
         \href{https://swtch.com/~rsc/regexp/regexp4.html}{\textcolor{blue}{design}}
         of Google Code Search.
       \item Replaced previous Static Index implementation and gained over 15x
         performance boost while providing more features such as advanced
         filtering for code completion-based symbol search.
       \item Reduced code completion symbol search average latency from
         \SI{16}{\mics} to \SI{1.09}{\mics} for LLVM codebase (3M Lines Of
         Code) and from \SI{119}{\mics} to \SI{1.9}{\mics} for Chromium
         codebase (16M LOC).
       \item Implemented Variable length Byte (VByte) compression algorithm and
         reduced memory overhead by 60\%.
       \item Identified performance bottlenecks in commonly used LLVM YAML
         serializer and improved performance by a factor of 3.
     \end{itemize}}
  \cventry{Jun 2016 - Sep 2016}{Software Engineering
    Intern}{Google}{}{C++ Language Tools Team}{
    Worked on Clang-Rename, Clang-based tool for renaming symbols such as
    variables, functions, arguments.
    \begin{itemize}
      \item Fixed a number of existing issues such as inconsistent renaming
        and lack of support for template classes, introduced new functionality
        and gained users for Clang-Rename.
      \item Built Vim and Emacs plugins for Clang-Rename tool.
      \item Designed and prototyped
        \href{https://docs.google.com/document/d/1w9IkR0_Gqmd5w4CZ2t_ZDZrNLYVirQPyMS41533HQZE/edit?usp=sharing}
        {\textcolor{blue}{clang-refactor}}, which later resulted in
        \href{https://clang.llvm.org/docs/RefactoringEngine.html}{\textcolor{blue}{Clang's
        Refactoring Engine}}.
      \item Started a discussion about building Language Server which later
        resulted in Clangd creation and became the main focus of the team.
      \item Added new checks to Clang-Tidy and reduced false-positive rate for
        existing ones.
    \end{itemize}}
  \cventry{Jun 2015 - Sep 2015}{Google Summer of Code student}{LLVM
    Community}{Remote}{}{Implemented Code Clone Detection tool in Clang Static
    Analyzer and used it to detect over 400 similar code pieces in Git,
    Vim, OpenSSL and other projects. GitHub page contains an
    \href{https://github.com/kirillbobyrev/code-clone-detection-llvm-devmtg15-poster\#code-clone-detection-llvm-devmtg15-poster}{\textcolor{blue}{overview}}
    of key results.}

\section{Projects}
  \cventry{2015 - Present}{LLVM}{Open Source Compiler Infrastructure
    Project}{}{}{Participating in LLVM-related projects and working on
    Clang-based C++ tooling. This includes contributing to Clangd, Clang-Tidy,
    Clang Static Analyzer and other C++ Language tools. My work has been
    featured multiple times on \href{http://llvmweekly.org/}{LLVM Weekly}
    covering the most important recent changes.
    \href{https://github.com/llvm/llvm-project/commits?author=kirillbobyrev}{\textcolor{blue}{List}}
    of all my commits.
    }

\renewcommand{\refname}{Publications \& Conference Talks}
\nocite{*}
\printbibliography

% TODO: List Soft Skills: Product Management, Deep User Interviews, ...
\section{Skills}
  \cvitem{Programming Languages}{Modern C++, Python, Rust, Haskell}
  \cvitem{Libraries}{LLVM, TensorFlow, Numpy, PyTorch}
  \cvitem{Competencies}{Compilers, Machine Learning: Deep Learning, Computer
    Vision, Reinforcement Learning, Algorithms and Data Structures}
  \cvitem{Software}{Linux, Git, LLDB, Tmux, \LaTeX, (Neo)Vim, VSCode}
  % TODO: Do a better job.
  \cvitem{Soft Skills}{Product Management, User Interviews,
    Interviewing candidates}
  \cvitem{Languages}{English (Fluent), Russian (Fluent), German (Advanced)}

\section{Education}
  \cventry{}{BSc}{Russia}{Moscow Institute of Physics and
    Technology}{Applied Mathematics and Physics}{}
  % TODO: Fill this in.
  \cventry{}{Yandex Management School}{}{Yandex}{Product and
    Project Management}{}

\end{document}
